Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2019-03-11 paper.tex
Fix electronic polarizabilities

\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Declan Scullion}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Dale Hughes}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\author{Lu Hua Li}
\affiliation{Institute for Frontier Materials, Deakin University, Waurn Ponds, Victoria, Australia}
\author{Chih-Jen Shih}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Jonathan Coleman}
\affiliation{School of Physics, Centre for Research on Adaptive Nanostructures and Nanodevices (CRANN) and Advanced Materials and BioEngineering Research (AMBER), Trinity College Dublin, Dublin 2, Ireland.}
\author{Manish Chhowalla}
%% \affiliation{Materials Science and Engineering, Rutgers University, 607 Taylor Road, Piscataway, New Jersey 08854, USA.}
\affiliation{Department of Materials Science \& Metallurgy, University of Cambridge, CB3 0FS, United Kingdom}
\author{Elton J. G. Santos}
\email{e.santos@qub.ac.uk}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\date{}
\title{Electric polarizability as the fundamental variable in the dielectric properties of two-dimensional materials}
%\title{The Unified Nature of the Dielectric Properties of Two-Dimensional Materials}
% \title{Unified Understanding of the Dielectric Nature of Two-Dimensional Materials}
\begin{document}

@@

$E_{\mathrm{g}}$ (blue dots) and 2D electric polarizabilities (bar

@@

Our results show that the 2D electric polarizability
$\alpha_{\mathrm{2D}}$ is a local variable determining the dielectric
properties of 2D materials.  There exist well defined relationships
between $\alpha_{\mathrm{2D}}$ and other quantities hidden in the
electronic properties.  According to our analysis, simple scaling
equations involving bandgaps and layer thicknesses can be used to
describe both dielectric and electronic features at the same
footing. A dielectric anisotropy index is found relating any material
dimension with its controllability.  Thus, our results suggest that
the challenge of understanding the dielectric phenomena is in general
a geometrical problem mediated by the bandgap. We believe the
principles presented here will benefit both fundamental understanding
of 2D materials as well as rational device design and optimization.

>>>>

\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Declan Scullion}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Dale Hughes}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\author{Lu Hua Li}
\affiliation{Institute for Frontier Materials, Deakin University, Waurn Ponds, Victoria, Australia}
\author{Chih-Jen Shih}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Jonathan Coleman}
\affiliation{School of Physics, Centre for Research on Adaptive Nanostructures and Nanodevices (CRANN) and Advanced Materials and BioEngineering Research (AMBER), Trinity College Dublin, Dublin 2, Ireland.}
\author{Manish Chhowalla}
%% \affiliation{Materials Science and Engineering, Rutgers University, 607 Taylor Road, Piscataway, New Jersey 08854, USA.}
\affiliation{Department of Materials Science \& Metallurgy, University of Cambridge, CB3 0FS, United Kingdom}
\author{Elton J. G. Santos}
\email{e.santos@qub.ac.uk}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\date{}
\title{Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials}
%\title{The Unified Nature of the Dielectric Properties of Two-Dimensional Materials}
% \title{Unified Understanding of the Dielectric Nature of Two-Dimensional Materials}
\begin{document}

@@

$E_{\mathrm{g}}$ (blue dots) and 2D electronic polarizabilities (bar

@@

Our results show that the 2D electronic polarizability
$\alpha_{\mathrm{2D}}$ is a local variable determining the dielectric
properties of 2D materials.  There exist well defined relationships
between $\alpha_{\mathrm{2D}}$ and other quantities hidden in the
electronic properties.  According to our analysis, simple scaling
equations involving bandgaps and layer thicknesses can be used to
describe both dielectric and electronic features at the same
footing. A dielectric anisotropy index is found relating any material
dimension with its controllability.  Thus, our results suggest that
the challenge of understanding the dielectric phenomena is in general
a geometrical problem mediated by the bandgap. We believe the
principles presented here will benefit both fundamental understanding
of 2D materials as well as rational device design and optimization.
